Morris Responses

### 2015-10-20 response/response.tex

% Reviewer 1: Q10
\begin{review}
In Sec. $3.2.1$ the authors remark that light used for night image acquisition does not influence plant development.
A reference should be included to support this statement.
\end{review}

\begin{response}
We have revised paragraph $2$ in Sec. $3.2.1$ and added $2$ references to support this statement.
\end{response}

% Reviewer 1: Q11
\begin{review}
As for the other lighting and imaging protocols adopted by the authors (Sec. $3.2.1$ and $3.2.2$), do they interfere with plant growth?
\end{review}

\begin{response}
RGB images are collected without additional light sources and only when the growth illumination is turned on, while the distance measurements uses a near IR ($\sim900~nm$) light sources.  
These modalities should not influence photosynthesis, growth or development.  
Both IR imaging and chlorophyll fluorescence imaging collect data during a very short dark interval when the growth light is electronically shuttered ($\sim100~microseconds/image$).  
This should have minimal impact on photosynthesis and presumably growth.  
Two saturating light flashes ($300~msec$ duration) in rapid succession ($\sim600~msec$ apart) are used during chlorophyll fluorescence imaging.  
At high frequency ($4$ or more image sets per hour), this modality can be damaging to photosynthesis and growth, especially at low growth light intensities when photoprotection is minimally induced.  
We have limited image collection to $1$ data set per hour.
\end{response}

@@

% Reviewer 1: Q19
\begin{review}
In Eq. $3$, p. $8$, the authors should better define the symbols used.
In particular, it is not clear if subscripts $1$ and $2$ refer to inner and outer leaf tips respectively, and in which order.
\end{review}

\begin{response}
$t_1$ represents the outer leaf tip and $t_2$ represents the inner leaf tip.
This representation is the same as the released leaf tip labels as illustrated in Sec. $4.4$.
%The equation does not rely on the correspondence of inner or outer tips as long as the estimated tips correspond to the labeled tips.
\end{response}

% Reviewer 1: Q20
\begin{review}
Sec. $5.1$, p. $9$, for completeness the authors should mention the approach they used to find a threshold for plant segmentation.
\end{review}

\begin{response}
We use some training images with ground truth plant segmentation masks to learn a threshold for binary segmentation.
The learnt threshold is then applied to both training images and testing images to generate the image mask.
We have added this statement to the paper.
\end{response}

@@

% Reviewer 2: Q36
\begin{review}
Figure $2$ if possible can you please also include an image showing the cameras from the view of the plant (LED off)?
\end{review}

\begin{response}
Figure $2$ is updated with extended details.
Please refer to the paper.
\end{response}

% Reviewer 2: Q37
\begin{review}
Collimated ... is a nice special term, but please put in parenthesis the definition to help broad readership.
\end{review}

\begin{response}
``Collimated" means to make the light rays parallel in order to minimize dispersion of light.
We have added this definition in the paper.
\end{response}

### 2015-10-20 response/morrisResponse.tex
all

\begin{response}
\todo{write response}
\end{response}

@@

\begin{response}
\todo{What does this question mean -- what is a supervisor?}
\end{response}

@@

\begin{response}
\todo{response similar to above}
\end{response}

>>>>

\begin{response}
We expanded our description of the labeling and the propagation to other modalities in the paper.  The data labeling is performed in the fluorescence image modality.  The infra-red image is from the same camera and so pixel labeling will be identical.  The labels are propagated to the color and depth modalities using planar homographies.  The homography between the fluorescence image and the color image is calculated by fitting matching features in these modalities, and the homography to the depth image is found by fitting a plane through the 3D plant points.  As the reviewer noted, using these homographies will result in pixel segmentation errors due to parallax for plant regions outside of the modeled planes.  We evaluate these errors qualitatively and quantitatively.  Figure~\ref{fig:LabelAlignment} illustrates the label propagations from the fluorescence image to the other modalities and from the color image to other modalities with two different line colors.  Errors occur where the lines fail to overlap and are due to propagation effects as well as boundary selection variations by the labeler between modalities.  We compare the magnitude of these two effects in table \todo{XXX}. \todo{ADD TABLE RESULTS}

\begin{figure*}
\begin{centering}
\begin{tabular}{cccc}
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_3_hour_23-seg_ir.png}&
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_3_hour_23-seg_fmp.png}&
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_3_hour_23-seg_rgb.png}&
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_3_hour_23-seg_depth.png}\\
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_5_hour_23-seg_ir.png}&
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_5_hour_23-seg_fmp.png}&
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_5_hour_23-seg_rgb.png}&
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_5_hour_23-seg_depth.png}\\
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_9_hour_20-seg_ir.png}&
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_9_hour_20-seg_fmp.png}&
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_9_hour_20-seg_rgb.png}&
\includegraphics[width=.18\textwidth]{../Figures/LabelAlignment/day_9_hour_20-seg_depth.png}\\
($a$) & ($b$) & ($c$) & ($d$) \\
\end{tabular}
\caption{Label propagation between all four modalities ($a$) infra-red, ($b$) fluorescence, ($c$) color and ($d$) depth, of a sample plant in the Arabidopsis collection for day 3 (top row), day 5 (middle row), and day 9 (bottom row).  In the dataset the manual segmentation is performed on the fluorescence images and is outlined here as orange lines propagated to all modalities.  The infra-red image is taken by the same camera and so will have close to exact pixel correspondence.  To assess the segmented pixel propagation to other modalities, we also manually labeled a subset of the color plant images and propagated this segmentation to all modalities (shown in cyan).  Comparing these boundaries in each modality gives a measure of the propagation errors due to parallax, and we provide quantitative analysis in table XXX.  Note that the color and depth images are rotated 90 degrees.}
\label{fig:LabelAlignment}
\end{centering}
\end{figure*}

\end{response}

@@

\begin{response}
We used an extra annotator. \todo{is this correct?}
\end{response}

@@

\begin{response}
The pixel correspondence accuracy evaluation is explained in a response above, and a figure has been added to illustrate it, (Figure~\ref{fig:LabelAlignment}). 
\end{response}
